Driver coverage

### 2024-02-07 scomatic/reports/driver_coverage.Rmd
add gains_and_losses report file

---
title: "Driver coverage"
author: "Alexandra Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_width: 8
    keep_md: false
    code_folding: show
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    theme: lumen
params:
  id: NULL
  depths: NULL
  drivers: NULL
  ref_cds: NULL
  cache_dir: './driver_coverage_cache/'
  rerun: true
---

@@

```{r read_cov}
# read coverage
cov <- xfun::cache_rds({
  cov <- 
    readr::read_tsv('depths.tsv') %>% 
    dplyr::mutate(chr = as.character(chr))
  cov
}, file = 'cov.rds', rerun = params$rerun)

@@

  cov %>% 
    dplyr::group_by(gene) %>%
    dplyr::group_split() %>%
    purrr::map(function(df_i) {

      # for testing:
      # cov %>% dplyr::group_by(gene) %>% dplyr::group_split() %>% {.[[1]]} -> df_i

      # get info
      gene_i <- unique(df_i$gene)
      p[[gene_i]] <<- list()

      # get number of celltypes for plot dims
      p[[gene_i]]$n_cts <<- 
        df_i %>% 
        dplyr::filter(!is.na(celltype)) %>% 
        dplyr::pull(celltype) %>% 
        dplyr::n_distinct()

@@

          # plot all
          p[[gene_i]][[paste0('all', p_suffix)]] <<-
            plot_all(
              p_df = lvl,
              p_exon_coords = exon_coords %>% dplyr::filter(gene == gene_i),
              p_title = paste0(gene_i, p_suffix)
            )

          # plot exons
          p[[gene_i]][[paste0('exons', p_suffix)]] <<-
            plot_exons(
              p_df = lvl,
              p_title = paste0(gene_i, p_suffix)
            )
        })
    })

>>>>

---
title: "Driver coverage"
author: "Alexandra Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_width: 8
    keep_md: false
    code_folding: show
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    theme: lumen
params:
  id: NULL
  drivers: NULL
  ref_cds: NULL
  cache_dir: './driver_coverage_cache/'
  rerun: true
---

@@

```{r read_cov}
# read coverage
cov <- xfun::cache_rds({
  cov <-
    list.files(pattern = '_depths.tsv') %>% 
    purrr::set_names(., gsub('_depths.tsv', '', .)) %>%
    purrr::map(function(file) {
      file %>%
        readr::read_tsv() %>%
        dplyr::mutate(chr = as.character(chr))
    }) %>%
    dplyr::bind_rows(.id = 'id')
  cov
}, file = 'cov.rds', rerun = params$rerun)

@@

  cov %>% 
    {split(., .$id)} %>%
    purrr::map(function(df_id) {

      # get id, inititate sublist
      id_i <- unique(df_id$id)
      p[[id_i]] <<- list()

      # go by gene
      df_id %>%
        {split(., .$gene)} %>%
        purrr::map(function(df_i) {

          # get gene, initiate sublist
          gene_i <- unique(df_gene$gene)
          p[[id_i]][[gene_i]] <<- list()

          # get number of celltypes for plot dims
          p[[id_i]][[gene_i]]$n_cts <<- 
            df_i %>% 
            dplyr::filter(!is.na(celltype)) %>% 
            dplyr::pull(celltype) %>% 
            dplyr::n_distinct()

@@

              # plot all
              p[[id_i]][[gene_i]][[paste0('all', p_suffix)]] <<-
                plot_all(
                  p_df = lvl,
                  p_exon_coords = exon_coords %>% dplyr::filter(gene == i),
                  p_title = paste0(i, p_suffix)
                )

              # plot exons
              p[[id_i]][[gene_i]][[paste0('exons', p_suffix)]] <<-
                plot_exons(
                  p_df = lvl,
                  p_title = paste0(i, p_suffix)
                )
            })
        })
    })
